---
title: "String manipulation using backreference wiht `Stringr` + `rebus`"
date: "`r Sys.Date()`"
layout: post
output:
  html_document
tags: [R]
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

In practice, `backreference` is an R function in `rebus`, which is useful for replacement operations. I will apply some functions in stringr with `backreference` by a Chinese lyric. 

## Example: Chinese Lyric

### Import a lyric

We can use the function `readLines` in `base`, but we have a better choice. That is, `stri_read_lines` in `stringi`, which is faster and
more stable.

```{r, message = FALSE}
library(stringi)
lyrics <- stri_read_lines("/Users/wen-tingwang/egpivo/_rmd/lyrics")
print(lyrics)
```


### View the Match patterns with repeated characters.

We want to see which character repeated twice in the lyric. We will view which line is matched.

```{r, message = FALSE, warning = FALSE}
library(stringr)
library(rebus)

# Define the pattern
pattern <- capture(WRD) %R% REF1

#View matches of pattern
str_view_all(lyrics, pattern = pattern , match = TRUE)
```

### Extract the mathced lines
Before we extracting matched lines,  we use `str_subset` to store subset of matched lines first. 

```{r}
lines <- str_subset(lyrics, pattern = pattern)
```
Then, we apply `str_extract` to extract the lines, and show the repeated characters.
```{r}
# Extract matches from lines
chr <- str_extract_all(lines, pattern = pattern)
# Show the frequencies of repeated characters
knitr::kable(plyr::count(chr[[1]]))
```

### View characters with a pair that reverses

```{r}
reverse <- capture(WRD) %R% capture(WRD) %R% REF2%R% REF1
str_view_all(lyrics, pattern = reverse, match = TRUE)
```

### Replace with backreferces
#### Build a pattern to be replaced
We build a pattern that finds a chines character "愛". We first check it against `lyrics`. 
```{r,}
replacePattern <- "愛"
str_view_all(lyrics, pattern = replacePattern)
```

#### Test out the replacement 
Then, we apply `str_replace_all` to replace the pattern with some words including '愛' and a unicode around it. 

```{r}
str_replace_all(lyrics, pattern = capture(replacePattern), str_c("\u2661", REF1, "\u2661", sep = ""))
```

## References
* DataCamp: [String Manipulation in R with stringr](https://www.datacamp.com/courses/string-manipulation-in-r-with-stringr).

## R Session

```{r session, echo = FALSE}
devtools::session_info()
```